Interval Probability for Fuzzy Quantum Theories

### 2016-07-09 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} Fix a bug...
prob.tex \subsection{Quantum Probability Measures} Explicitly write down the connection between the Radon-Nikodym theorem and Gleason's theorem

Although specifying a probability for every event looks complex, a
probability measure can be simply constructed by $\pmeas(E)=\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in E}}\rho(\omega)$,
where $\rho:\Omega\rightarrow[0,1]$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in\Omega}}\rho(\omega)=1$.
Furthermore, every probability measure~$\pmeas$ can be written in
this form for an unique $\rho$~\cite{Kolmogorov1950,Swart2013}.
This fact is a special case of the the Radon-Nikodym theorem, and
$\rho$ is called the Radon-Nikodym derivative of $\pmeas$ with respect
to the counting measure~\cite{Nikodym1930,Folland2013}. For example,
the Radon-Nikodym derivative of $\pmeas$ in example~\ref{ex1} is:
\[
\begin{array}{rcl}
\rho\left(HH\right)=1/3,\quad\rho\left(HT\right)=0,\quad\rho\left(TH\right)=2/3,\quad\rho\left(TT\right)=0\textrm{ .}\end{array}
\]

@@

Like a classical probability measure can be easily defined by its
Radon-Nikodym derivative, a quantum probability measure can be easily
constructed by states according to the Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007}.
For each pure normalized ($\ip{\phi}{\phi}=1$) quantum state $\ket{\phi}$,
the Born rule induces a probability measure $\mu_{\phi}^{B}$ as follows:
\[
\mu_{\phi}^{B}(P)=\ip{\phi}{P\phi}\textrm{ .}
\]

@@

@@

\begin{example}[Three-dimensional quantum interval-valued probability
measure] Given a three dimensional Hilbert space with an orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Consider\emph{
$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}, $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
and $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$. Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(1-\proj{0})=\bar{\mu}(1-\proj{\ps})=\bar{\mu}(1-\proj{\ps'}) & = & \necess\textrm{ ,}\\
\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
\end{eqnarray*}
To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
it is sufficient to check $\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$
for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. This is easily
verified by enumerating all possible cases.

>>>>

Although specifying a probability for every event looks complex, a
probability measure can be simply constructed by 
\begin{equation}
\pmeas(E)=\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in E}}\rho(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
\end{equation}
where $\rho:\Omega\rightarrow[0,1]$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in\Omega}}\rho(\omega)=1$.
Furthermore, every probability measure~$\pmeas$ can be written in
this form for an unique $\rho$~\cite{Kolmogorov1950,Swart2013}.
This fact is a special case of the the Radon-Nikodym theorem, and
$\rho$ is called the Radon-Nikodym derivative of $\pmeas$ with respect
to the counting measure~\cite{Nikodym1930,Folland2013}. For example,
the Radon-Nikodym derivative of $\pmeas$ in example~\ref{ex1} is:
\[
\begin{array}{rcl}
\rho\left(HH\right)=1/3,\quad\rho\left(HT\right)=0,\quad\rho\left(TH\right)=2/3,\quad\rho\left(TT\right)=0\textrm{ .}\end{array}
\]

@@

A quantum probability measure can be easily constructed by states
according to the Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007}.
For each pure normalized ($\ip{\phi}{\phi}=1$) quantum state $\ket{\phi}$,
the Born rule induces a probability measure $\mu_{\phi}^{B}$ as follows:
\[
\mu_{\phi}^{B}(P)=\ip{\phi}{P\phi}\textrm{ .}
\]

@@

Actually, constructing a quantum probability measures from a density
matrix~$\rho$ is similar to defining a classical probability measure
by its Radon-Nikodym derivative. This can be seen more easily if we
pick an orthonormal basis~$\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
such that $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\psi_{j}\in S}}\proj{\psi_{j}}$,
where $S$ is the linear subspace $P$ projects onto. Then, a density
matrix~$\rho$ can also be represented in the same basis, i.e., $\rho=\sum_{i=1}^{d}\sum_{j=1}^{d}r_{ij}\proj{\psi_{j}}$,
and the Born rule becomes
\begin{eqnarray}
\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{\psi_{j}\in S}r_{jj}\textrm{ ,}\label{BornRule.mixed-1}
\end{eqnarray}
which is basically the same as equation (\ref{eq:Radon-Nikodym}).

@@

\begin{example}[Three-dimensional quantum interval-valued probability
measure] Given a three dimensional Hilbert space with an orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Consider\emph{
$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}, $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
and $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$. Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'}) & = & \necess\textrm{ ,}\\
\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
\end{eqnarray*}
To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
it is sufficient to check $\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$
for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. This is easily
verified by enumerating all possible cases.
